Post CMOS technologies: An Overview and Analysis

### 2025-06-04 Paper.tex
bibs
idk what changes i made

\subsection{Threshold Logic Gate}
A threshold logic gate is a gate that outputs a high signal if 
an input signal surpasses a certain threshold and outputs low 
otherwise. To give an example simply, imagine the input had a range 
of voltages from 0-9 and there is a threshold voltage of 5. Any
input voltage above high will output a binary high signal from the 
gate and any voltage below will output a low signal. A TLG 
is oftentimes also used to analyze a weighted sum from its inputs 
and see if that is above the threshold.

@@

\subsubsection{Memristor-Based Threshold Logic Gate}
da

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

\subsubsection{Threshold Logic Gate}
A threshold logic gate is a gate that outputs a high signal if 
an input signal surpasses a certain threshold and outputs low 
otherwise. To give an example simply, imagine the input had a range 
of voltages from 0-9 and there is a threshold voltage of 5. Any
input voltage above high will output a binary high signal from the 
gate and any voltage below will output a low signal. A TLG 
is oftentimes also used to analyze a weighted sum from its inputs 
and see if that is above the threshold.

@@

\subsubsection{Memristor-Based Threshold Logic Gate}
Memristors are ideal for TLG implementation since their variable 
resistance can act as programmable weights. A common architecture
for a memristor based TLG implements a hybrid architecture with 
memristors and traditional CMOS components into two main parts:
a differential part and a sensor part.

The differential part is where a memristor is actually used. Each 
memristor is paired with a transistor known as a 1T1M array.
Here an input and reference threshold signal is taken in. When a 
voltage is then applied as the input current flows through the
memristor. The memristor here acts as a knob that controls how much 
current is passed through this differential part. This part 
can also be switched off when not in use to save power.

The current from the differential part then goes to the sensor. 
The sensor compares a combined current coming from either one or 
multiple differential parts and sees if its above the threshold. 
Based on this comparison either a 1 or 0 is outputted indicating 
whether the sum of the weights have surpassed the threshold. 
%\cite here%

\subsubsection{Challenges}
Despite the theoretical efficiency of memristor based TLGs, 
their practical implementation still face significant challenges. 
Fabrication is still very difficult and there are no EDA tools 
compatible with designing devices made of memristors TLGs.

\subsection{Hardware Implementation of Memristor-Based Artificial Neural Networks}
Beyond logic gates, memristors are particularly compelling for 
neural networks due to their inherent ability to perform efficient 
vector matrix multiplicaton which serves as the backbone of 
modern neural networks.

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
